\pkg{Rgbp}: An R Package for Gaussian, Poisson, and Binomial Hierarchical Modeling

### 2013-08-03 jss/article.tex
changes

As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight. This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree of prior and observed information respectively. If the second level has more information than the first level, then the estimator will shrink towards the prior mean more than 50\%. This is clear in this example because, as caseload increases, shrinkage decreases, depending less on the second-level information.

@@

From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23. Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow less information from other hospitals. The result being that the upper bound of the $95\%$ interval is smaller.

@@

In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are practically indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates for this particular dataset have a good repeated sampling property.

>>>>

As we can see in (\ref{gammapost}), the posterior mean, $(1-B_{j})y_{j} + B_{j}\lambda_{0}$, is a convex combination of the sample mean and prior mean ($\lambda_{0}=0.02$) with the shrinkage factor, $B_{j}\equiv r / (r + n_{j})$, determining the weight. This makes intuitive sense because $r$ and $n_{j}$ can be interpreted as the degree of prior and observed information respectively. If the second level has more information than the first level, \emph{i.e.} ensemble sample size $r$ exceeds individual sample size $n_{j}$, then the estimator will shrink towards the prior mean more than 50\%. This is clear in this example because, as caseload increases, shrinkage decreases, depending less on the second-level information.

@@

From the output provided by \code{gbp} it can be seen that a reasonable choice of a hospital for the patient is hospital 23. Although hospital 8 has a smaller observed mean the fact that hospital 23 has a much higher caseload means that we borrow relatively less information from other hospitals. The result being that the upper bound of the $95\%$ interval is smaller.

@@

In Figure \ref{fig:hospitalcoverage} we see two estimated coverage probabilities: a simple unbiased estimate (a blue dashed line) and an Rao-Blackwellized unbiased estimate (a red line). Both lines are practically indistinguishable from the horizontal line at 0.95 and the estimated overall average coverage rate is 0.950 from the Rao-Blackwellized estimate. This result shows that the interval estimates for this particular dataset accurately achieves 95\% confidence under repeated sampling.
